---
title: "Homework03"
format: html
editor: visual
---

# Set Up

```{r}
#| label: Set Up
#| message: false
library(tidyverse)
library(here)
library(janitor)
library(readxl)
salinity <- read_csv(
  here(
    "data",
    "salinity-pickleweed.csv"
  ))
my_data <- read_csv(
  here(
    "data",
    "my_data Sheet2.csv"
  ))
```

[html link](https://samarx27.github.io/ENVS-193DS_homework-03/)

# Problem 1. Slough Soil Salinity

## a.

A Pearson's correlation test would determine the strength of the relationship between salinity and California pickleweed biomass because this type of correlation is meant for continuous, normally distributed variables. 

## b.

## c.

## d.

## e.

## f.

# Problem 2. Personal Data

## a.
```{r}
#| label: Jitter Plot displaying wake up time for school and non school days
my_data_clean <- my_data |> #labeling new data frame
clean_names() #cleaned names to only include lower case letters and underscores
ggplot(data = my_data_clean, #using my_data_clean data frame
aes(x = school_day_yes_no, #placing school_day_yes_no on the x-axis
y = wake_up_time_hrs_min, #placing wake_up_time_hrs_min on the y-axis
color = school_day_yes_no)) + #color by school_day_yes_no
geom_boxplot() + #creating a boxplot
labs(x = "School Day", #labeling the x-axis as School Day
y = "Wake Up time (hrs:min)", #labeling the y-axis as Wake Up time (hrs:min)
title = "Wake Up Time for School Days vs Non-School Days", #creating title
subtitle = "03/01/2026") + #creating subtitle
geom_jitter() + #creating jittered points
theme_light() + #changing theme to light
scale_color_manual(values = c("yes" = "blue4",
"no" = "red4")) + #changing colors based on whether or not it is a school day
theme(legend.position = "none") #removing the legend
```

```{r}
#| label: Time series plot for wake up time for each day
ggplot(data = my_data_clean, #determining data frame
aes(x = date, #placing these observations on the x-axis
y = wake_up_time_hrs_min)) + #placing these observations on the x-axis
geom_point(color = "gold") + #making the points gold
labs(x = "Date", #labeling the x-axis
y = "Wake Up time (hrs:min)", #labeling the y-axis
title = "Wake Up Time for Each Day", #creating a title
subtitle = "03/01/2026") + #creating a subtitle
theme_light() #changing the theme to light
```

## b.
Figure 1. This figure shows the distribution of recorded wake up times between school days, which is denoted by the blue points, and non-school days, which is denoted by the red points. Additionally, the figure shows the medians and quartiles for each type of day, represented by the boxes and lines, indicating that the median wake up time is later on non-school days than on school days. 

Figure 2. This figure shows the distribution of recorded wake up times for each day from 01/25/2026 to 03/01/2026, denoted by the gold points.

# Problem 3. Affective Visualization

## a. 
I think an affective visualization could look be similar to figure two, where instead of the points and axis, it could look like a sunrise where each point is supposed to fall, given that the data is showing when I wake up. 

## b. 

## c. 

## d. 

## e. 

# Problem 4. Statistical Critique 

## a. 

## b. 

## c. 

## d. 